### 2023-03-29 response-to-audit-report.md

+### Variations from Isabelle Semantics
+
+Marlowe's semantics validator uses Plutus's association list `PlutuxTx.AssocMap` that differs from the `MList` in Isabelle semantics in several respects:
+
+1.  The `insert`, `delete`, `member`, and `lookup` functions of `AssocMap` haven an equality (`Eq`) constraint whereas `MList` has a ordering (`Ord`) constraint.
+2.  If the elements of an `MList` are not in lexicographic order, then result of `insert`, `delete`, `member`, and `lookup` may differ from that in `AssocMap`.
+3.  The ordering of the result of `toList` may differ between `AssocMap` and `MList`.
+
+Provided that the initial state of the Marlowe contract does not contain duplicate entries in `accounts`, `choices`, or `boundValues` and also provided that the behavior of Marlowe's semantics validator is compared to Isabelle semantics with the Isabelle initial state for `accounts`, `choices`, and `boundValues` lexicographic ordered, the behavior of the Marlowe semantics validator does not differ from Isabelle semantics aside from the ordering of `accounts`, `choices`, and `boundValues` in Marlowe's state in the datum. Typically, Marlowe contracts start with an empty state, so this is not an issue, but one can in principle start a Marlowe contract with a non-empty state, even with one that contains duplicate entries. Internally to the validator, `computeTransaction` might order payments upon `Close` differently from Isabelle semantics, but that is undetectable at the validation or transaction level.
+
+
 ## Merkelization

 A contract can be represented as a tree of continuations ("sub-contracts") where each vertex is a contract and each edge follows either an `InputContent` made by a participant or a timeout. A `When` contract includes terms that are either (1) a `Case` which contains the `Action` that matches a particular `InputContent` via `NormalInput` and that explicitly includes the `Contract` continuation or (2) a `MerkleizedCase` which contains the `Action` that matches a particular `InputContent` via `MerkleizedInput` and that implicitly includes the continuation by reference to its Merkle hash. In the latter case `MerkleizedInput` includes both the Merkle hash of the continuation and the continuation `Contract` itself. The Plutus code must verify that the hash in the contract matches the hash in the input before it proceeds to use the continuation that was provided as input.

+Merkleization enables large contracts to be succinctly represented on chain: instead of storing gigabytes of data representing a huge contract, only the hash of that contract need be represented on the chain. For example, a contract `When [Case action timeout continuation] contract'` that validates input `TransactionInput interval [NormalInput input]` may be "merkleized" to a contract `When [MerkleizedCase action hash] contract'` that will validate the input `TransactionInput interval [MerkleizedInput input hash contract]` provided that `DatumHash hash ≡ datumHash . Datum . toBuiltinData $ contract`. When a contract is merkelized the information `(hash, contract)` is stored off chain and provide to the Marlowe validator if needed for input. The Cardano node computes the hash and provides the `(hash, contract)` information in the script context.
+
 The Isabelle semantics do not include merkleization of Marlowe contracts, but the Haskell implementation does.

@@ -108,7 +130,7 @@ The Isabelle semantics do not include merkleization of Marlowe contracts, but th

 The Marlowe validator is an unparameterized interpreter of Marlowe semantics. Thus, the script address of the Marlowe validator is independent of the particular contract instance and roles currency.
 ```haskell
-smallMarloweValidator :: MarloweData -> MarloweInput -> ScriptContext -> Bool
+marloweValidator :: MarloweData -> MarloweInput -> ScriptContext -> Bool
 ```

@@ -127,7 +149,7 @@ data MarloweData =
 data MarloweParams =
     MarloweParams
     {
-      rolePayoutValidatorHash :: ValidatorHash
+      rolesCurrency :: CurrencySymbol
     }
 ```

@@ -139,14 +161,17 @@ data MarloweTxInput =
     Input InputContent
   | MerkleizedTxInput InputContent BuiltinByteString
 ```
-In the above, the `BuiltinByteString` is the hash of the serialized continuation of the contract. If `MerkleizedTxInput` is supplied in a redeemer, then the `ScriptContext` for the transaction must also contain an extra entry in its `txInfoData . scriptContextTxInfo` map from `DatumHash` to `Datum` for the serialized continuation of the contract.
+In the above, the `BuiltinByteString` is the hash of the serialized continuation of the contract. If `MerkleizedTxInput` is supplied in a redeemer, then the `ScriptContext` for the transaction must also contain an extra entry in its `txInfoData . scriptContextTxInfo` map from `DatumHash` to `Datum` for the serialized continuation of the contract. Thus the `continuation` for a given `hash` is computed as follows:
+```haskell
+Just continuation = fromBuiltinData =<< lookup hash (txInfoData $ scriptContextTxInfo scriptContext) :: Maybe Contract
+```

 ### A Note about `Plutus.V1.Ledger.Value`

 This specification relies on the following properties of `Plutus.V1.Ledger.Value` in the `plutus-ledger-api` package:
 1. `instance Monoid Value`, where `mempty` is zero value for all tokens and `mappend` sums the amounts of corresponding token types.
-2. `leq` is a partial ordering requiring that quantity of each token in the first operand is less than or equal to quanity of the corresponding token in the second operand, where a missing token in one operand represents a zero quantity.
+2. `leq` is a partial ordering requiring that quantity of each token in the first operand is less than or equal to quantity of the corresponding token in the second operand, where a missing token in one operand represents a zero quantity.

 ### Relationship between Marlowe Validator and Semantics
@@ -156,9 +181,10 @@ The arguments of `computeTransaction` must be constructed as follows:
 2. The `txInputs` of `TransactionInput` is derived from the `MarloweInput` provided as the `Redeemer` and the `txInfoData . scriptContextTxInfo` of the `ScriptContext`, as detailed below.
 3. The `State` is the `marloweState` of the `MarloweData` provided as the `Datum`.
 4. The `Contract` is the `marloweContract` of the `MarloweData` provided as the `Datum`.
-5. The new `Datum` at the script address is the `MarloweData` with the same `marloweParams` as originally, but with the new `txOutState` and `txOutContract` of the `TransactionOutput`.

-In the diagram below, the upper three rectangles represent functions: the untyped `Validator`, the typed validator `smallMarloweValidator`, or the semantics's `computeTransaction`. The data values (ovals) are marshalled or passed from the untyped representation over to the semantics. The `computeTransaction` function validates the semantics and returns the required new state and contract instance. Conceptually, success or failure is passed to the untyped validator. The bottom rectangle packages the `Datum` that is provided as output for the continued progression of the Marlowe contract instance.
+Additionally, the new `Datum` at the script address is the `MarloweData` with the same `marloweParams` as originally, but with the new `txOutState` and `txOutContract` of the `TransactionOutput`.
+
+In the diagram below, the upper three rectangles represent functions: the untyped `Validator`, the typed validator `marloweValidator`, or the semantics's `computeTransaction`. The data values (ovals) are marshalled or passed from the untyped representation over to the semantics. The `computeTransaction` function validates the semantics and returns the required new state and contract instance. Conceptually, success or failure is passed to the untyped validator. The bottom rectangle packages the `Datum` that is provided as output for the continued progression of the Marlowe contract instance.

 ![Relationship between Marlowe validator and semantics.](semantics2plutus.svg)

@@ -167,7 +193,7 @@ In the diagram below, the upper three rectangles represent functions: the untype

 Consider the application of the Marlowe validator and Marlowe semantics:
 ```haskell
-validationResult = smallMarloweValidator marloweData marloweInput scriptContext
+validationResult = marloweValidator marloweData marloweInput scriptContext

 transactionOutput = computeTransaction transactionInput inState inContract
 ```
@@ -241,12 +267,14 @@ inValue ≡ foldMap toValue (accounts $ marloweState marloweData)

 #### *Constraint 6.* Output value to script

-The beginning balance plus the deposits equals the ending balance plus the payments.
+The beginning balance plus the deposits (with negative deposits treated as zero, as required by the semantics) equals the ending balance plus the payments.
 ```haskell
 inValue + foldMap valueOfDeposit (fmap getInputContent transactionInput) ≡ outValue + foldMap valueOfPayment (txOutPayments transactionOutput)
   where getInputContent (Input inputContent) = inputContent
         getInputContent (MerkleizedTxInput inputContent _) = inputContent
-        valueOfDeposit (IDeposit _ _ (Token currency name) count) = Value.singleton currency name count
+        valueOfDeposit (IDeposit _ _ (Token currency name) count)
+          | count > 0 = Value.singleton currency name count
+          | otherwise = mempty
         valueOfDeposit _ = mempty
         valueOfPayment (Payment _ (Party _) value)) = value
         valueOfPayment _ = mempty
@@ -302,12 +330,16 @@ all demerkleizes transactionInput ≡ True
         demerkleizes (Input _) = True
 ```

+Note that this constraint is not strictly necessary and is included here for informational purposes, since a valid transaction could not be constructed if it were removed.
+

 #### *Constraint 13.* Positive balances

-All accounts in the state have positive balances.
+All accounts in the initial and final states have positive balances.
 ```haskell
-all ((> 0) . snd) (accounts $ marloweState marloweData) ≡ True
+positiveBalances $ marloweState marloweData     ≡ True
+positiveBalances $ txOutState transactionOutput ≡ True
+  where positiveBalances state = all ((> 0) . snd) (accounts state)
 ```

@@ -345,6 +377,38 @@ all sufficient (txOutPayments transactionOutput)

 Note that the comparison is `leq` instead of equality because additional Ada may be required in the payment in order to satisfy the ledger's `minimum UTxO` constraint.

+The payment to a role must be in a single output, but the payment to an address may be split in multiple outputs, so long as the total output to the address is sufficient. (Note that allowing the multiple outputs to an address may increase transaction fees and wallet fragmentation, but the magnitude of this is severely limited by the Plutus execution budget, which strongly depends upon the number of UTxOs output. The flexibily of multiple outputs accommodates wallet-related practicalities (e.g., limitations in coin-selection and transaction balancing) such as the change and the return of the role token being in separate UTxOs in situations where a contract is also paying to the address where that change and that role token are sent.)
+
+
+#### *Constraint 18.* Final balance
+
+The value output to the script's UTxO must equal the total value in the output state.
+```haskell
+outValue ≡ foldMap toValue (accounts $ txOutState transactionOutput)
+  where toValue ((_, Token currency name), count)) = Value.singleton currency name count
+```
+
+
+#### *Constraint 19.* No duplicates
+
+The initial and final state must not have duplicate keys in their account entries, choices, or bound values.
+```haskell
+hasDuplicateKey (accounts    inState ) ≡ False
+hasDuplicateKey (choices     inState ) ≡ False
+hasDuplicateKey (boundValues inState ) ≡ False
+hasDuplicateKey (accounts    outState) ≡ False
+hasDuplicateKey (choices     outState) ≡ False
+hasDuplicateKey (boundValues outState) ≡ False
+  where
+    outState = txOutState transactionOutput
+    hasDuplicateKey am = let ks = fst <$> toList am in length ks /= length (nub ks)
+```
+
+
+#### *Constraint 20.* Single satisfaction
+
+If the contract makes payments, then the Marlowe validator must be the only validator executing in the transaction.
+

 ## Plutus Validator for Marlowe Payouts

@@ -359,7 +423,7 @@ rolePayoutValidator :: (CurrencySymbol, TokenName) -> () -> ScriptContext -> Boo

 Consider the application of the Marlowe payout validator:
 ```haskell
-validationResult' = rolePayoutValidator rolesCurrency' role () scriptContext
+validationResult' = rolePayoutValidator (rolesCurrency', role) () scriptContext
 ```

 The validation fails (via returning `False` for `validationResult'` or via the throwing of an error) if any of the following constraints does not hold.
```

### Post-Audit Changes in Marlowe Validator

```bash
git diff 523f3d56f22bf992ddb0b0c8a52bb7a5a188f9e9 69468d6623e24a4ccd6659e378ae012c38ca01ce marlowe/src/Language/Marlowe/{Core/V1/Semantics*,Scripts.hs}
```

```diff
diff --git a/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs b/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
index e31b8c478..82b57b903 100644
--- a/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
+++ b/marlowe/src/Language/Marlowe/Core/V1/Semantics.hs
@@ -94,12 +94,12 @@ module Language.Marlowe.Core.V1.Semantics
   , TransactionError(..)
   , TransactionWarning(..)
     -- * Utility Functions
+  , allBalancesArePositive
   , contractLifespanUpperBound
   , isClose
   , notClose
   , paymentMoney
   , totalBalance
-  , validateBalances
     -- * Serialisation
   , currencySymbolFromJSON
   , currencySymbolToJSON
@@ -217,6 +217,26 @@ import Text.PrettyPrint.Leijen (comma, hang, lbrace, line, rbrace, space, text,
 data Payment = Payment AccountId Payee Token Integer
   deriving stock (Haskell.Eq, Haskell.Show)

+instance ToJSON Payment where
+  toJSON (Payment accountId payee token amount) =
+    object
+      [
+        "payment_from" .= accountId
+      , "to" .= payee
+      , "token" .= token
+      , "amount" .= amount
+      ]
+
+instance FromJSON Payment where
+  parseJSON =
+    withObject "Payment"
+      $ \o ->
+        Payment
+          <$> o .: "payment_from"
+          <*> o .: "to"
+          <*> o .: "token"
+          <*> o .: "amount"
+

 -- | Extract the money value from a payment.
 paymentMoney :: Payment -> Money
@@ -293,7 +313,28 @@ data TransactionError = TEAmbiguousTimeIntervalError
                       | TEUselessTransaction
                       | TEHashMismatch
   deriving stock (Haskell.Show, Generic, Haskell.Eq)
-  deriving anyclass (ToJSON, FromJSON)
+
+instance ToJSON TransactionError where
+  toJSON TEAmbiguousTimeIntervalError = JSON.String "TEAmbiguousTimeIntervalError"
+  toJSON TEApplyNoMatchError = JSON.String "TEApplyNoMatchError"
+  toJSON (TEIntervalError intervalError) = object ["error" .= JSON.String "TEIntervalError", "context" .= intervalError]
+  toJSON TEUselessTransaction = JSON.String "TEUselessTransaction"
+  toJSON TEHashMismatch = JSON.String "TEHashMismatch"
+
+instance FromJSON TransactionError where
+  parseJSON (JSON.String s) =
+    case s of
+      "TEAmbiguousTimeIntervalError" -> return TEAmbiguousTimeIntervalError
+      "TEApplyNoMatchError" -> return TEApplyNoMatchError
+      "TEUselessTransaction" -> return TEUselessTransaction
+      "TEHashMismatch" -> return TEHashMismatch
+      _ -> Haskell.fail "Failed parsing TransactionError"
+  parseJSON (JSON.Object o) = do
+                                err <- o .: "error"
+                                if err Haskell.== ("TEIntervalError" :: Haskell.String)
+                                  then TEIntervalError <$> o .: "context"
+                                  else Haskell.fail "Failed parsing TransactionError"
+  parseJSON _ = Haskell.fail "Failed parsing TransactionError"

 -- | Marlowe transaction input.
@@ -319,6 +360,31 @@ data TransactionOutput =
     | Error TransactionError
   deriving stock (Haskell.Show)

+instance ToJSON TransactionOutput where
+  toJSON TransactionOutput{..} =
+    object
+      [
+        "warnings" .= txOutWarnings
+      , "payments" .= txOutPayments
+      , "state" .= txOutState
+      , "contract" .= txOutContract
+      ]
+  toJSON (Error err) = object ["transaction_error" .= err]
+
+instance FromJSON TransactionOutput where
+  parseJSON =
+    withObject "TransactionOutput"
+      $ \o ->
+        let
+          asTransactionOutput =
+            TransactionOutput
+              <$> o .: "warnings"
+              <*> o .: "payments"
+              <*> o .: "state"
+              <*> o .: "contract"
+          asError = Error <$> o .: "transaction_error"
+        in
+          asTransactionOutput <|> asError

### 2023-03-29 response-to-audit-report.md

 -- | Parse a validator hash from JSON.
 validatorHashFromJSON :: JSON.Value -> Parser ValidatorHash
@@ -404,12 +470,22 @@ evalValue env state value = let
                                    then 0
                                    else n `Builtins.quotientInteger` d
         ChoiceValue choiceId ->
+            -- SCP-5126: Given the precondition that `choices` contains no
+            -- duplicate entries, this lookup behaves identically to
+            -- Marlowe's Isabelle semantics given the precondition that
+            -- the initial state's `choices` in Isabelle was sorted and
+            -- did not contain duplicate entries.
             case Map.lookup choiceId (choices state) of
                 Just x  -> x
                 Nothing -> 0
         TimeIntervalStart    -> getPOSIXTime (fst (timeInterval env))
         TimeIntervalEnd      -> getPOSIXTime (snd (timeInterval env))
         UseValue valId       ->
+            -- SCP-5126: Given the precondition that `boundValues` contains
+            -- no duplicate entries, this lookup behaves identically to
+            -- Marlowe's Isabelle semantics given the precondition that
+            -- the initial state's `boundValues` in Isabelle was sorted
+            -- and did not contain duplicate entries.
             case Map.lookup valId (boundValues state) of
                 Just x  -> x
                 Nothing -> 0
@@ -425,6 +501,11 @@ evalObservation env state obs = let
         AndObs lhs rhs          -> evalObs lhs && evalObs rhs
         OrObs lhs rhs           -> evalObs lhs || evalObs rhs
         NotObs subObs           -> not (evalObs subObs)
+                                   -- SCP-5126: Given the precondition that `choices` contains no
+                                   -- duplicate entries, this membership test behaves identically
+                                   -- to Marlowe's Isabelle semantics given the precondition that
+                                   -- the initial state's `choices` in Isabelle was sorted and did
+                                   -- not contain duplicate entries.
         ChoseSomething choiceId -> choiceId `Map.member` choices state
         ValueGE lhs rhs         -> evalVal lhs >= evalVal rhs
         ValueGT lhs rhs         -> evalVal lhs > evalVal rhs
@@ -439,6 +520,12 @@ evalObservation env state obs = let
 refundOne :: Accounts -> Maybe ((Party, Token, Integer), Accounts)
 refundOne accounts = case Map.toList accounts of
     [] -> Nothing
+    -- SCP-5126: The return value of this function differs from
+    -- Isabelle semantics in that it returns the least-recently
+    -- added account-token combination rather than the first
+    -- lexicographically ordered one. Also, the sequence
+    -- `Map.fromList . tail . Map.toList` preserves the
+    -- invariants of order and non-duplication.
     ((accId, token), balance) : rest ->
         if balance > 0
         then Just ((accId, token, balance), Map.fromList rest)
@@ -447,18 +534,30 @@ refundOne accounts = case Map.toList accounts of

 -- | Obtains the amount of money available an account.
 moneyInAccount :: AccountId -> Token -> Accounts -> Integer
-moneyInAccount accId token accounts = case Map.lookup (accId, token) accounts of
-    Just x  -> x
-    Nothing -> 0
+moneyInAccount accId token accounts =
+    -- SCP-5126: Given the precondition that `accounts` contains
+    -- no duplicate entries, this lookup behaves identically to
+    -- Marlowe's Isabelle semantics given the precondition that
+    -- the initial state's `accounts` in Isabelle was sorted and
+    -- did not contain duplicate entries.
+    case Map.lookup (accId, token) accounts of
+      Just x  -> x
+      Nothing -> 0

 -- | Sets the amount of money available in an account.
 updateMoneyInAccount :: AccountId -> Token -> Integer -> Accounts -> Accounts
 updateMoneyInAccount accId token amount =
+    -- SCP-5126: Given the precondition that `accounts` contains
+    -- no duplicate entries, this deletion or insertion behaves
+    -- identically (aside from internal ordering) to Marlowe's
+    -- Isabelle semantics given the precondition that the initial
+    -- state's `accounts` in Isabelle was sorted and did not
+    -- contain duplicate entries.
     if amount <= 0 then Map.delete (accId, token) else Map.insert (accId, token) amount

--- | Add the given amount of money to an accoun (only if it is positive).
+-- | Add the given amount of money to an account (only if it is positive).
 --   Return the updated Map.
 addMoneyToAccount :: AccountId -> Token -> Integer -> Accounts -> Accounts
 addMoneyToAccount accId token amount accounts = let
@@ -482,6 +581,14 @@ giveMoney accountId payee token amount accounts = let
 reduceContractStep :: Environment -> State -> Contract -> ReduceStepResult
 reduceContractStep env state contract = case contract of

+    -- SCP-5126: Although `refundOne` refunds accounts-token combinations
+    -- in least-recently-added order and Isabelle semantics requires that
+    -- they be refunded in lexicographic order, `reduceContractUntilQuiescent`
+    -- ensures that the `Close` pattern will be executed until `accounts`
+    -- is empty. Thus, the net difference between the behavior here and the
+    -- Isabelle semantics is that the `ContractQuiescent` resulting from
+    -- `reduceContractUntilQuiescent` will contain payments in a different
+    -- order.
     Close -> case refundOne (accounts state) of
         Just ((party, token, amount), newAccounts) -> let
             newState = state { accounts = newAccounts }
@@ -522,7 +629,17 @@ reduceContractStep env state contract = case contract of
     Let valId val cont -> let
         evaluatedValue = evalValue env state val
         boundVals = boundValues state
+        -- SCP-5126: Given the precondition that `boundValues` contains
+        -- no duplicate entries, this insertion behaves identically
+        -- (aside from internal ordering) to Marlowe's Isabelle semantics
+        -- given the precondition that the initial state's `boundValues`
+        -- in Isabelle was sorted and did not contain duplicate entries.
         newState = state { boundValues = Map.insert valId evaluatedValue boundVals }
+        -- SCP-5126: Given the precondition that `boundValues` contains
+        -- no duplicate entries, this lookup behaves identically to
+        -- Marlowe's Isabelle semantics given the precondition that the
+        -- initial state's `boundValues` in Isabelle was sorted and did
+        -- not contain duplicate entries.
         warn = case Map.lookup valId boundVals of
               Just oldVal -> ReduceShadowing valId oldVal evaluatedValue
               Nothing     -> ReduceNoWarning
@@ -575,6 +692,11 @@ applyAction env state (IDeposit accId1 party1 tok1 amount) (Deposit accId2 party
     else NotAppliedAction
 applyAction _ state (IChoice choId1 choice) (Choice choId2 bounds) =
     if choId1 == choId2 && inBounds choice bounds
+    -- SCP-5126: Given the precondition that `choices` contains no
+    -- duplicate entries, this insertion behaves identically (aside
+    -- from internal ordering) to Marlowe's Isabelle semantics
+    -- given the precondition that the initial state's `choices`
+    -- in Isabelle was sorted and did not contain duplicate entries.
     then let newState = state { choices = Map.insert choId1 choice (choices state) }
          in AppliedAction ApplyNoWarning newState
     else NotAppliedAction
@@ -592,18 +714,20 @@ getContinuation (MerkleizedInput _ inputContinuationHash continuation) (Merkleiz
     else Nothing
 getContinuation _ _ = Nothing

--- | Try to apply an input to a list of cases.
+-- | Try to apply an input to a list of cases, accepting the first match.
 applyCases :: Environment -> State -> Input -> [Case Contract] -> ApplyResult
-applyCases env state input (headCase : tailCase) =
+applyCases env state input (headCase : tailCases) =
     let inputContent = getInputContent input :: InputContent
         action = getAction headCase :: Action
         maybeContinuation = getContinuation input headCase :: Maybe Contract
     in case applyAction env state inputContent action of
          AppliedAction warning newState ->
+           -- Note that this differs from Isabelle semantics because
+           -- the Cardano semantics includes merkleization.
            case maybeContinuation of
              Just continuation -> Applied warning newState continuation
              Nothing           -> ApplyHashMismatch
-         NotAppliedAction -> applyCases env state input tailCase
+         NotAppliedAction -> applyCases env state input tailCases
 applyCases _ _ _ [] = ApplyNoMatchError

@@ -615,7 +739,7 @@ applyInput _ _ _ _                          = ApplyNoMatchError

 -- | Propagate 'ReduceWarning' to 'TransactionWarning'.
 convertReduceWarnings :: [ReduceWarning] -> [TransactionWarning]
-convertReduceWarnings = foldr (\warn acc -> case warn of
+convertReduceWarnings = foldr (\warn acc -> case warn of  -- Note that `foldr` is used here for efficiency, differing from Isabelle.
     ReduceNoWarning -> acc
     ReduceNonPositivePay accId payee tok amount ->
         TransactionNonPositivePay accId payee tok amount : acc
@@ -655,12 +779,12 @@ applyAllInputs env state contract inputs = let
                     curState
                     cont
                 (input : rest) -> case applyInput env curState input cont of
-                    Applied applyWarn newState cont ->
+                    Applied applyWarn newState cont' ->
                         applyAllLoop
                             True
                             env
                             newState
-                            cont
+                            cont'
                             rest
                             (warnings' ++ convertApplyWarning applyWarn)
                             payments'
@@ -759,8 +883,8 @@ totalBalance accounts = foldMap

 -- | Check that all accounts have positive balance.
-validateBalances :: State -> Bool
-validateBalances State{..} = all (\(_, balance) -> balance > 0) (Map.toList accounts)
+allBalancesArePositive :: State -> Bool
+allBalancesArePositive State{..} = all (\(_, balance) -> balance > 0) (Map.toList accounts)

 instance FromJSON TransactionInput where
@@ -845,20 +969,26 @@ instance Eq Payment where
 instance Eq ReduceWarning where
     {-# INLINABLE (==) #-}
     ReduceNoWarning == ReduceNoWarning = True
-    (ReduceNonPositivePay acc1 p1 tn1 a1) == (ReduceNonPositivePay acc2 p2 tn2 a2) =
+    ReduceNoWarning == _ = False
+    ReduceNonPositivePay acc1 p1 tn1 a1 == ReduceNonPositivePay acc2 p2 tn2 a2 =
         acc1 == acc2 && p1 == p2 && tn1 == tn2 && a1 == a2
-    (ReducePartialPay acc1 p1 tn1 a1 e1) == (ReducePartialPay acc2 p2 tn2 a2 e2) =
+    ReduceNonPositivePay{} == _ = False
+    ReducePartialPay acc1 p1 tn1 a1 e1 == ReducePartialPay acc2 p2 tn2 a2 e2 =
         acc1 == acc2 && p1 == p2 && tn1 == tn2 && a1 == a2 && e1 == e2
-    (ReduceShadowing v1 old1 new1) == (ReduceShadowing v2 old2 new2) =
+    ReducePartialPay{} == _ = False
+    ReduceShadowing v1 old1 new1 == ReduceShadowing v2 old2 new2 =
         v1 == v2 && old1 == old2 && new1 == new2
-    _ == _ = False
+    ReduceShadowing{} == _ = False
+    ReduceAssertionFailed == ReduceAssertionFailed = True
+    ReduceAssertionFailed == _ = False

 instance Eq ReduceEffect where
     {-# INLINABLE (==) #-}
     ReduceNoPayment == ReduceNoPayment           = True
+    ReduceNoPayment == _                         = False
     ReduceWithPayment p1 == ReduceWithPayment p2 = p1 == p2
-    _ == _                                       = False
+    ReduceWithPayment _ == _                     = False

 -- Lifting data types to Plutus Core
diff --git a/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs b/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
index a333b8fbb..bf495773b 100644
--- a/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
+++ b/marlowe/src/Language/Marlowe/Core/V1/Semantics/Types.hs
@@ -108,7 +108,7 @@ import PlutusTx.Lift (makeLift)
 import PlutusTx.Prelude hiding (encodeUtf8, mapM, (<$>), (<*>), (<>))
 import Prelude (mapM, (<$>))
 import qualified Prelude as Haskell
-import Text.PrettyPrint.Leijen (text)
+import Text.PrettyPrint.Leijen (parens, text)

 -- Functions that used in Plutus Core must be inlinable,
@@ -126,8 +126,8 @@ data Party =
   deriving stock (Generic,Haskell.Eq,Haskell.Ord)

 instance Pretty Party where
-  prettyFragment (Address network address) = text $ "Address " ++ Haskell.show (serialiseAddressBech32 network address)
-  prettyFragment (Role role)               = text $ "Role "    ++ Haskell.show role
+  prettyFragment (Address network address) = parens $ text "Address " Haskell.<> prettyFragment (serialiseAddressBech32 network address)
+  prettyFragment (Role role)               = parens $ text "Role "    Haskell.<> prettyFragment role

 instance Haskell.Show Party where
   showsPrec _ (Address network address) = Haskell.showsPrec 11 $ Haskell.show (serialiseAddressBech32 network address)
@@ -307,6 +307,13 @@ data State = State { accounts    :: Accounts
 newtype Environment = Environment { timeInterval :: TimeInterval }
   deriving stock (Haskell.Show,Haskell.Eq,Haskell.Ord)

+instance FromJSON Environment where
+  parseJSON = withObject "Environment"
+    (\v -> Environment <$> (posixIntervalFromJSON =<< v .: "timeInterval"))
+
+instance ToJSON Environment where
+  toJSON Environment{..} = object
+    [ "timeInterval" .= posixIntervalToJSON timeInterval]

 -- | Input for a Marlowe contract. Correspond to expected 'Action's.
 data InputContent = IDeposit AccountId Party Token Integer
@@ -389,23 +396,24 @@ data IntervalError = InvalidInterval TimeInterval
                    | IntervalInPastError POSIXTime TimeInterval
   deriving stock (Haskell.Show, Generic, Haskell.Eq)

+
 instance ToJSON IntervalError where
   toJSON (InvalidInterval (s, e)) = A.object
-    [ ("invalidInterval", toJSON (posixTimeToJSON s, posixTimeToJSON e)) ]
+    [ ("invalidInterval", A.object [("from", posixTimeToJSON s), ("to", posixTimeToJSON e)]) ]
   toJSON (IntervalInPastError t (s, e)) = A.object
-    [ ("intervalInPastError", toJSON (posixTimeToJSON t, posixTimeToJSON s, posixTimeToJSON e)) ]
+    [ ("intervalInPastError", A.object [("minTime", posixTimeToJSON t), ("from", posixTimeToJSON s), ("to", posixTimeToJSON e)]) ]

 instance FromJSON IntervalError where
   parseJSON (JSON.Object v) =
     let
       parseInvalidInterval = do
-        (s, e) <- v .: "invalidInterval"
-        InvalidInterval <$> ((,) <$> posixTimeFromJSON s <*> posixTimeFromJSON e)
+        o <- v .: "invalidInterval"
+        InvalidInterval <$> posixIntervalFromJSON o
       parseIntervalInPastError = do
-        (t, s, e) <- v .: "intervalInPastError"
+        o <- v .: "intervalInPastError"
         IntervalInPastError
-          <$> posixTimeFromJSON t
-          <*> ((,) <$> posixTimeFromJSON s <*> posixTimeFromJSON e)
+          <$> (posixTimeFromJSON =<< o .: "minTime")
+          <*> posixIntervalFromJSON o
     in
       parseIntervalInPastError <|> parseInvalidInterval
   parseJSON invalid =
@@ -422,11 +430,18 @@ posixTimeFromJSON = \case
   invalid ->
       JSON.prependFailure "parsing POSIXTime failed, " (JSON.typeMismatch "Number" invalid)

+posixIntervalFromJSON :: A.Object -> Parser TimeInterval
+posixIntervalFromJSON o = (,) <$> (posixTimeFromJSON =<< o .: "from") <*> (posixTimeFromJSON =<< o .: "to")

 -- | Serialise time as a JSON value.
 posixTimeToJSON :: POSIXTime -> JSON.Value
 posixTimeToJSON (POSIXTime n) = JSON.Number $ scientific n 0

+posixIntervalToJSON :: TimeInterval -> JSON.Value
+posixIntervalToJSON (from, to) = object
+  [ "from" .= posixTimeToJSON from
+  , "to" .= posixTimeToJSON to
+  ]

 -- | Result of 'fixInterval'
 data IntervalResult = IntervalTrimmed Environment State
@@ -778,23 +793,24 @@ instance ToJSON Contract where
 instance Eq Party where
     {-# INLINABLE (==) #-}
     Address n1 a1 == Address n2 a2 = n1 == n2 && a1 == a2
+    Address _ _   == _             = False
     Role r1       == Role r2       = r1 == r2
-    _             == _             = False
+    Role _        == _             = False

 instance Eq ChoiceId where
     {-# INLINABLE (==) #-}
-    (ChoiceId n1 p1) == (ChoiceId n2 p2) = n1 == n2 && p1 == p2
+    ChoiceId n1 p1 == ChoiceId n2 p2 = n1 == n2 && p1 == p2

 instance Eq Token where
     {-# INLINABLE (==) #-}
-    (Token n1 p1) == (Token n2 p2) = n1 == n2 && p1 == p2
+    Token n1 p1 == Token n2 p2 = n1 == n2 && p1 == p2

 instance Eq ValueId where
     {-# INLINABLE (==) #-}
-    (ValueId n1) == (ValueId n2) = n1 == n2
+    ValueId n1 == ValueId n2 = n1 == n2

 instance Pretty ValueId where
@@ -804,78 +820,107 @@ instance Pretty ValueId where
 instance Eq Payee where
     {-# INLINABLE (==) #-}
     Account acc1 == Account acc2 = acc1 == acc2
+    Account{}    == _            = False
     Party p1 == Party p2         = p1 == p2
-    _ == _                       = False
+    Party{}  == _                = False
